---
title: "AGILE 2019 PhD School Proceedings"
author: "Daniel Nüst"
date: "`r Sys.time()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document provides some scripts and documentation of manual steps for generating the AGILE 2019 PhD School Proceedings for CEUR-WS.

## Get the repos

```{r paths}
library("here")
article_repos <- here::here("article_repos")
article_pdfs <- here::here("submission/ceur-ws")
```

To update a specific article, simply delete the corresponding directory from `r article_repos`.

```{r article_repos}
# read from repos.txt
library("tibble")
library("dplyr")
library("stringr")

articles <- as_tibble(read.csv2(here::here("repos.txt"), comment.char = "#", stringsAsFactors = FALSE)) %>%
  dplyr::mutate(id = stringr::str_replace_all(.$author, "[;\\.,\\s]", "_")) %>%
  dplyr::mutate(path = file.path(article_repos, .$id)) %>%
  arrange(id)

# clone repos
library("gert")

for (i in 1:nrow(articles)) {
  repo <- articles[i,]
  path <- repo$path
  if(dir.exists(path))
    next()
  
  dir.create(path, showWarnings = FALSE)
  cat("Cloning for", repo$author, "from", repo$work_repo, "to", path, "\n")
  gert::git_clone(url = paste0("https://github.com/", repo$work_repo), path = path)
}
```

## Create a PDF for each repo

```{r ceur_template, eval=FALSE, include=FALSE}
# notes and testing of template usage
library("rmarkdown")

remotes::install_local("template/ceurticles")
```

1. identify "main file"
2. add header to files if missing?
3. create PDFs for each article using the template in the R package `template/ceurticles`

```{r rmd_file}
rmd_file <- function(p) {
  candidates <- list.files(p, pattern = "\\.Rmd", ignore.case = TRUE)
  if(length(candidates) > 1) {
    warning("Found more than one R Markdown file in ", p, "\n\t", toString(candidates), "\n\tUsing: ", candidates[[1]], "\n\n")
    return(candidates[[1]])
  }
  if(length(candidates) < 1) {
    warning("Found NO R Markdown file in ", p, "\n\n")
    return(NA)
  }
  else {
    return(candidates)
  }
}

articles$rmd_file <- unlist(sapply(articles %>% arrange(id) %>% .$path, rmd_file))
#articles
```

```{r knit}
library("rmarkdown")
library("rticles")
# remotes::install_local("template/ceurticles")
library("ceurticles")

dir.create(article_pdfs, showWarnings = FALSE)

template_dir <- tempdir()
if (!file.exists(file.path(template_dir, "article.Rmd")))
  rmarkdown::draft(file.path(template_dir, "article.Rmd"), template = "twocolpceurws_article", package = "ceurticles", edit = FALSE, create_dir = FALSE)
#list.files(template_dir)

copy_article_files <- function(article) {
  file.copy(file.path(template_dir, c("copyright.tex",
                                      "twocolpceurws.sty",
                                      "samplebib.bib")),
            article$path, overwrite = TRUE)
}

copy_article_files(article = articles[1,])

# TODO do for all papers
```

**Now manually make sure that the R Markdown files compile.**

Here is a template header with the required fields.
Note that the `bibliography`, even if no references are used, must be set.
The authors' `affiliation`, `orcid` and `email` are optional.

```yaml
---
title: "AGILE PhD School working notes"
author:
  - name: Alexander Kmoch
    affiliation: University of Tartu, Estonia
    email: alexander.kmoch@ut.ee
    orcid: 0000-0003-4386-4450
  - name: Evelyn Uuemaa
    affiliation: University of Tartu, Estonia
    orcid: 0000-0002-0782-6740
abstract: |
   TODO abstract here
output:
  ceurticles::twocolpceurws_article
bibliography: samplebib.bib
---
```

```{r render_single}
render_article_file <- function(article) {
  output_file <- file.path(article_pdfs, paste0(article$id, ".pdf"))
  cat("Rendering article", file.path(article$path, article$rmd_file), "to", output_file, "\n")
  
  rmarkdown::render(file.path(article$path, article$rmd_file),
                    output_file = output_file)
}

render_article_file(articles[1,])

# TODO do for all papers
```

## Create CEUR-WS proceedings

Based on **http://ceur-ws.org/HOWTOSUBMIT.html**

### Generate the table of contents

1. Install [`ceur-make`](https://github.com/ceurws/ceur-make)
  - On Ubuntu install `libsaxonhe-java` and find the location of the `.jar` file with `dpkg -L libsaxonhe-java` (or get the JAR from somewhere else)
  - Create the submission files from the directory of `ceur-make`
    `./ceur-make-init ~/git/agile_2019_phd_school_proceedings/submission`
  - Adjust `Makefile.vars` with path to SAXON HE
3. Enter all information in `submission/workshop.xml` _manually_
3. Enter all information in `submission/toc.xml` _with the script below_
   ```{r toc}
   # RUN MANUALLY
   library("glue")
   author_template <- '<author>{author}</author>'
   paper_template <- '<paper id="{id}">
         <title>{title}</title>
         <authors>
           {authors}
         </authors>
     </paper>'
   
   generate_toc_entry <- function(article) {
     article_yaml <- rmarkdown:::yaml_front_matter(file.path(article$path, article$rmd_file))
     authors <- paste0(glue::glue_data(
                            list(author = sapply(article_yaml$author,
                                                 function(a) { a$name })),
                            author_template),
                       collapse = "\n      ")
     glue::glue_data(list(title = article_yaml$title,
                          id = article$id,
                          authors = authors),
                     paper_template)
   }
   
   toc <- c(
     generate_toc_entry(articles[1,])
   )
   
   # TODO do for all papers
   
   writeLines(c("<toc>",
                toc,
                "</toc>"),
              con = file("submission/toc.xml"))
   ```
3. Create submission directory with `ceur-make`
   ```bash
   cd submission
   make ceur-ws/index.html ceur-ws/temp.bib
   ```

### Prepare the submission file

1. Double check `index.html`
1. Check `submission/ceur-ws/temp.bib` and rename it to `AGILEPHD2019.bib`
2. HTML Validation
   > _You can check the consistency/completeness of the submission directory by accessing it locally with your Web browser, and we require you to validate it using [the W3C Validator](https://validator.w3.org/nu). If you use RDFa tags, we ask you to validate your RDFa by using [the W3C RDFa parser](http://www.w3.org/2012/pyRdfa/)._

### Submit with the "Upload (Procedure PUT)"

1. Check http://ceur-ws.org/HOWTOSUBMIT.html#TOPERRORS
1. Create a release tag, https://github.com/agilephdschool2019/agile_2019_phd_school_proceedings/releases
2. Create the submission ZIP file as documented by CEUR (see above)
3. Upload the submission ZIP to the release
4. Upload a ZIP with the signed agreements to another place
4. Send the link to the PDF to CEUR [via Email](ceurws@sunsite.informatik.rwth-aachen.de)
  - Subject: `CEURWS submission: (workshop acronym)`
  - Content:
    - URL of submission directory with ZIP files for the submission and the signed agreements
    - Your contact details

## Metadata

```{r metadata}
sessionInfo()
```

