---
title: "AGILE 2019 PhD School Proceedings"
author: "Daniel Nüst"
date: "`r Sys.time()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document provides some scripts and documentation of manual steps for generating the AGILE 2019 PhD School Proceedings.
They use a PDF template of CEUR-WS.
For some additional steps to submit these proceedigns _to_ CEUR-WS see [`ceur.md`](ceur.Rmd).

## Get the repos

```{r paths}
library("here")
article_repos <- here::here("article_repos")
article_pdfs <- here::here("articles")
```

To update a specific article, simply delete the corresponding directory `r rmarkdown::relative_to(dir = here(), article_repos)`

```{r article_repos}
# read from repos.txt
library("tibble")
suppressPackageStartupMessages(library("dplyr"))
library("stringr")
library("rmarkdown")

articles <- as_tibble(read.csv2(here::here("repos.txt"), comment.char = "#",
                                stringsAsFactors = FALSE)) %>%
  dplyr::mutate(id = stringr::str_replace_all(.$author, "[;\\.,\\s]", " ") %>%
                  stringr::str_replace_all(
                    c('ü' = 'ue', 'ï' = 'ie', 'ë' = 'ee', 'ä' = 'ae',
                      'ö' = 'oe', 'š' = 's', 'í' = 'i', 'ř' = 'r')) %>%
                  stringr::str_squish() %>%
                  stringr::str_replace_all(" ", "_")) %>%
  dplyr::mutate(path = file.path(article_repos, .$id)) %>%
  arrange(id)

# clone repos
suppressPackageStartupMessages(library("gert"))

for (i in 1:nrow(articles)) {
  repo <- articles[i,]
  path <- repo$path
  if(dir.exists(path)) {
    cat("Skipping existing directory ", rmarkdown::relative_to(dir = here(), path), "\n")
    next()
  }
  
  dir.create(path, showWarnings = FALSE)
  cat("Cloning for", repo$author, "from", repo$work_repo, "to", path, "\n")
  gert::git_clone(url = paste0("https://github.com/", repo$work_repo), path = path)
}
```

## Create a PDF for each repo

We use a template based on CEUR-WS's two-column format.
**Note**: The proceedings footer is _hardcoded_ in the file `template/ceurticles/inst/rmarkdown/templates/twocolpceurws_article/skeleton/copyright.tex`.
To include updates in the footer, the packages is always removed as part of the workflow.
For changes in the footer to trickle down into the PDFs, the article repo(s) must be removed.

```{r template}
remove.packages("ceurticles")
remotes::install_local("template/ceurticles", force = TRUE, dependencies = FALSE)
```

1. Identify "main file"
2. For each article
  1. Copy template files using the template in the R package `template/ceurticles` to the paper directory
  2. Render document

```{r rmd_file}
rmd_file <- function(p) {
  candidates <- list.files(p, pattern = "\\.Rmd$", ignore.case = TRUE)
  if(length(candidates) > 1) {
    warning("Found more than one R Markdown file in ", p, "\n\t",
            toString(candidates), "\n\tUsing: ", candidates[[1]], "\n\n")
    return(candidates[[1]])
  }
  if(length(candidates) < 1) {
    warning("Found NO R Markdown file in ", p, "\n\n")
    return(NA)
  }
  else {
    return(candidates)
  }
}

articles$rmd_file <- unlist(sapply(articles %>% arrange(id) %>% .$path, rmd_file))
```

```{r articles}
library("kableExtra")

articles %>%
  dplyr::mutate(path = sapply(articles$path,
                              rmarkdown::relative_to, dir = here(),
                              USE.NAMES = FALSE)) %>%
  knitr::kable(format = "latex") %>%
  kableExtra::kable_styling(latex_options="scale_down")
```

```{r copy_template_files}
library("rmarkdown")
library("rticles")
library("ceurticles")

dir.create(article_pdfs, showWarnings = FALSE)

template_dir <- tempdir()
if (!file.exists(file.path(template_dir, "article.Rmd")))
  rmarkdown::draft(file.path(template_dir, "article.Rmd"),
                   template = "twocolpceurws_article", package = "ceurticles",
                   edit = FALSE, create_dir = FALSE)

copy_article_files <- function(article) {
  file.copy(file.path(template_dir, c("copyright.tex",
                                      "twocolpceurws.sty",
                                      "samplebib.bib")),
            article$path, overwrite = FALSE)
}

#copy_article_files(article = articles[1,])

for (i in 1:nrow(articles)) {
  copy_article_files(article = articles[i,])
}
```

**Now manually make sure that the R Markdown files compile.**

Here is a template header with the required fields.
Note that the `bibliography`, even if no references are used, must be set.
The authors' `affiliation`, `orcid` and `email` are optional.

```yaml
---
title: "AGILE PhD School working notes"
author:
  - name: Alexander Kmoch
    affiliation: University of Tartu, Estonia
    email: alexander.kmoch@ut.ee
    orcid: 0000-0003-4386-4450
  - name: Evelyn Uuemaa
    affiliation: University of Tartu, Estonia
    orcid: 0000-0002-0782-6740
abstract: |
   TODO abstract here
output:
  ceurticles::twocolpceurws_article
bibliography: samplebib.bib
---
```

```{r render_articles, results='hide'}
render_article_file <- function(article) {
  output_file <- file.path(article_pdfs, paste0(article$id, ".pdf"))
  cat("Rendering article", file.path(article$path, article$rmd_file),
      "to", output_file, "\n")
  
  rmarkdown::render(file.path(article$path, article$rmd_file),
                    output_file = output_file)
}

#render_article_file(articles[14,])

for (i in 1:nrow(articles)) {
  render_article_file(article = articles[i,])
}
```

```{r list_files}
list.files(article_pdfs)
```

## Publish proceedings

Zenodo bla bla

https://doi.org/10.5281/zenodo.3835767

## Metadata

```{r metadata}
sessionInfo()
```
