---
title: "Create CEUR-WS proceedings"
author: "Daniel Nüst"
date: "`r Sys.time()`"
output:
  pdf_document: default
  html_document: default
---

Based on **http://ceur-ws.org/HOWTOSUBMIT.html**

## Prepare files

See `/articles` for the PDFs of the articles.
Copy them into a folder `/submission/ceur-ws`.

## Generate the table of contents

1. Install [`ceur-make`](https://github.com/ceurws/ceur-make)
  - On Ubuntu install `libsaxonhe-java` and find the location of the `.jar` file with `dpkg -L libsaxonhe-java` (or get the JAR from somewhere else)
  - Create the submission files from the directory of `ceur-make`, using
  
    `./ceur-make-init ~/git/agile_2019_phd_school_proceedings/submission`
  - Adjust `Makefile.vars` with path to SAXON HE
3. Enter all information in `submission/workshop.xml` _manually_
3. Enter all information in `submission/toc.xml` _with the script below_
```{r toc}
suppressPackageStartupMessages(library("glue"))

author_template <- '<author>{author}</author>'
paper_template <- '<paper id="{id}">
      <title>{title}</title>
      <authors>
        {authors}
      </authors>
  </paper>'

generate_toc_entry <- function(article) {
  article_yaml <- rmarkdown:::yaml_front_matter(file.path(article$path, article$rmd_file))
  authors <- paste0(glue::glue_data(
                         list(author = sapply(article_yaml$author,
                                              function(a) { a$name })),
                         author_template),
                    collapse = "\n      ")
  glue::glue_data(list(title = article_yaml$title,
                       id = article$id,
                       authors = authors),
                  paper_template)
}

tocs <- c()
for (i in 1:nrow(articles)) {
  tocs <- c(tocs, generate_toc_entry(article = articles[i,]))
}

toc_file <- file("submission/toc.xml")
writeLines(c("<toc>",
             tocs,
             "</toc>"),
           con = toc_file)
close(toc_file)
```
3. Create submission in submission directory with `ceur-make`

```{bash ceur-make}
cd submission
make ceur-ws/index.html ceur-ws/temp.bib
mv ceur-ws/temp.bib ceur-ws/AGILEPHD2019.bib
```

## Prepare the submission file

1. Double check `submission/ceur-ws/index.html` and `submission/ceur-ws/AGILEPHD2019.bib`
2. HTML Validation: _"You can check the consistency/completeness of the submission directory by accessing it locally with your Web browser, and we require you to validate it using [the W3C Validator](https://validator.w3.org/nu). If you use RDFa tags, we ask you to validate your RDFa by using [the W3C RDFa parser](http://www.w3.org/2012/pyRdfa/)."_

**Note:** If you make any changes in the directory `submission/ceur-ws`, you must manually recreate the ZIP file!

```{r zipfile}
submission_file <- here::here("submission/agilephd2019.zip")
file.remove(submission_file)
zip(zipfile = submission_file, files = "submission/ceur-ws")
```

## Submit with the "Upload (Procedure PUT)"

1. Check http://ceur-ws.org/HOWTOSUBMIT.html#TOPERRORS
1. Create a release tag, https://github.com/agilephdschool2019/agile_2019_phd_school_proceedings/releases
3. Upload the submission ZIP `r ` to some public share
4. Upload a ZIP with the signed agreements to some public share
4. Send the link to the submission archive to CEUR [via Email](ceurws@sunsite.informatik.rwth-aachen.de)
  - Subject: `CEURWS submission: AGILE PhD School 2019`
  - Content:
    - URLs of the aforementioned ZIP files
    - Your contact details
